---
title: "Scatterplot with different variables"
author: "hugominze"
date: "`r Sys.Date()`"
output: html_document 
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Scatterplot with different variables

This app creates a scatter plot with 2 different variables from the mtcars dataset. In the side panel, you are able to choose the variables for the x- and y-axis.

```{r, echo = FALSE}
library(shiny)
library(ggplot2)
shinyApp(

ui <- fluidPage(

        sidebarLayout(

                # Inputs: Select variables to plot
                sidebarPanel(

                        # Select variable for y-axis
                        selectInput(
                                inputId = "y",
                                label = "Y-axis:",
                                choices = c("mpg", "cyl", "disp", "hp", "drat", "wt", "qsec", "vs", "am", "gear", "carb"),
                                selected = "mpg"
                        ),
                        # Select variable for x-axis
                        selectInput(
                                inputId = "x",
                                label = "X-axis:",
                                choices = c("mpg", "cyl", "disp", "hp", "drat", "wt", "qsec", "vs", "am", "gear", "carb"),
                                selected = "cyl"
                        )
                ),

                # Output: Show scatterplot
                mainPanel(
                        h2("Scatterplot with different variables"),
                        p("Below you can see a scatterplot which plots 2 different variables from the mtcars dataset. In the side panel, you can choose the variables for the x- and y-axis."),
                        plotOutput(outputId = "scatterplot")

                )
        )
),

server <- function(input, output, session) {
        output$scatterplot <- renderPlot({
                ggplot(data = mtcars, aes_string(x = input$x, y = input$y)) +
                        geom_point()
        })
},

  options = list(height = 500)
)
```

## mtcars dataset

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

## columns

- [, 1]	mpg	Miles/(US) gallon
- [, 2]	cyl	Number of cylinders
- [, 3]	disp	Displacement (cu.in.)
- [, 4]	hp	Gross horsepower
- [, 5]	drat	Rear axle ratio
- [, 6]	wt	Weight (1000 lbs)
- [, 7]	qsec	1/4 mile time
- [, 8]	vs	Engine (0 = V-shaped, 1 = straight)
- [, 9]	am	Transmission (0 = automatic, 1 = manual)
- [,10]	gear	Number of forward gears
- [,11]	carb	Number of carburetors

## Head and dimensions

```{r}
head(mtcars)
```

